\documentclass[margin, line]{res}
\usepackage{helvet}
\usepackage{hyperref}
\usepackage[date=year, style=authoryear, minnames=3]{biblatex}
\addbibresource{cv.bib}

\textheight=700pt
\newsectionwidth{1.5in}

\begin{document}
\name{Daniel Severo}
\address{\textbf{For more information}: \url{https://dsevero.com}}
\begin{resume}
\section{SHORT BIO}
Graduate student with 5 terms of experience TAing, 3 years as a Data Scientist in Brazil, and 2 years as a Machine Learning Engineer implementing solutions in PyTorch for healthcare applications. Vector Institute scholarship recipient. Research intern at Facebook AI Research (FAIR) working on lossless data compression.

\section{EDUCATION}
\textbf{University of Toronto}\\
{\sl Electrical \& Computer Engineering}\\
Doctor of Philosophy (M.A.Sc. to Ph.D. transfer)\hfill Started Fall 2020\\
Undergraduate Exchange Program (1 year)\hfill 2013 - 2014

\textbf{Federal University of Santa Catarina}, Brazil\hfill 2010 - 2015 \\
{\sl Bachelor of Science in Electronics Engineering}\\
First Class Honours, 99th percentile.

\section{TEACHING EXPERIENCE}
\textbf{Federal University of Santa Catarina}\\
{\sl Teaching Assistant}\\
\begin{itemize}
    \item \textbf{Communications Theory} \hfill Fall and Winter 2015\\
Amplitude and frequency modulations; multiplexing; noise in communication systems; pulse modulation; analog-to-digital conversion; digital transmission in baseband and passband.
    \item \textbf{Introduction to Electronics} \hfill Fall and Winter 2013\\
Operational amplifiers; diodes; the bipolar junction transistor; field effect transistors; optoelectronic components.
    \item \textbf{Single-Variable Calculus} \hfill Fall 2010\\
Real-valued functions; limits; continuity; derivatives and applications; definite and indefinite integrals; integration techniques; improper integrals.
\end{itemize}

\textbf{CERTI Foundation} \hfill 2010 - 2013\\
{\sl Intern Programming Instructor}\\
Responsible for the technical training of new and current interns. Created a training course in LabVIEW programming that is still in use as of 2021.

\section{PUBLICATIONS}
\nocite{Severo2021-cf}
\nocite{Ruan2021-xb}
\nocite{Reys2020-su}
\printbibliography[heading=none]
* Equal contribution

\section{AWARDS}
\textbf{Vector Scholarship in Artificial Intelligence Recipient 2020-21} \hfill 2020\\
The Vector Scholarship in AI supports the recruitment of top students to AI-related master’s programs in Ontario and is valued at \$17,500.\\
\url{https://vectorinstitute.ai/aimasters}
\newpage
\textbf{NSERC Applied Research Rapid Response to COVID-19 Grant}\hfill 2020\\
Our project titled "Canadian Hospital Simulator For Management of COVID19 Cases and Contact Tracing" was awarded \$75,000.00.\\
\url{https://www.nserc-crsng.gc.ca/Innovate-Innover/CCI-COVID_eng.asp}

\textbf{Virtual Design Challenge Winner} \hfill 2019\\
Won 1st place at the VDC hosted by The University of British Columbia with my paper \emph{Proof of Novelty}. Received a cash prize of \$3,000.\\
\url{https://github.com/dsevero/Proof-of-Novelty}

\textbf{Student Merit Award and Medal} \hfill 2015\\
Graduated with the highest GPA ever obtained (at the time) for my major. Elected "Best Student" by the faculty of Electrical \& Electronics Engineering at the Federal University of Santa Catarina.

\textbf{Science Without Borders Scholarship} \hfill 2013\\
Awarded a full scholarship that covered tuition, transportation, necessary materials and living costs to study 2 academic semesters at the University of Toronto.

\section{PROFESSIONAL EXPERIENCE}

\textbf{Facebook AI Research (FAIR)} \hfill Summer 2021\\
{\sl Research Intern}

\textbf{Independent Contractor} \hfill 2018 - 2021\\
{\sl Machine Learning Engineer \& Researcher}

\textbf{Linx Impulse} \hfill 2016 - 2018\\
{\sl Head of Data Science}

\textbf{CERTI Foundation} \hfill 2015 - 2016\\
{\sl Research Engineer}

\textbf{Wavetech Technology Solutions} \hfill 2015\\
{\sl Engineering Intern}

\textbf{CERTI Foundation} \hfill 2010 - 2013\\
{\sl Engineering Intern}

\textbf{WEG Industries}  \hfill Summers 2011 and 2012\\
{\sl Engineering Intern}


\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}

\end{resume}
\(\)\end{document}
